Walk Through the Petri-Net In TiKZ Tutorial

### 2019-12-16 mstemc/index.tex
trivial udpate

% Intended LaTeX compiler: pdflatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
                  \usetikzlibrary{arrows,decorations.pathmorphing}
                  \usetikzlibrary{backgrounds,positioning,fit,petri}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Walk Through the Petri-Net In TiKZ Tutorial}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
 pdfkeywords={},
 pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\newcommand*{\titleCM}{\begingroup
\begin{center}
\vspace{\baselineskip}
{\Huge \textbf {Walk Through the Petri-Net In TiKZ Tutorial} \par}
\vspace{2\baselineskip}   \newline
{\large Eason Zhang with www.makesteamclear.com \par}
\vspace{\baselineskip}          \newline
{\large \today \par}
\vspace{\baselineskip}
\vfill
\setlength{\unitlength}{3pt}
\makebox[\textwidth][c]{\includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/example3.pdf}}
\vfill
\vspace{\baselineskip}
{\Large \href{WWW.MAKESTEAMCLEAR.COM}{WWW.MAKESTEAMCLEAR.COM} \par}\newline
\vspace{\baselineskip}
{\texttt www.makesteamclear.com is a free project, supported by Eason Zhang, to make videos about STEAM in a more approachable and different way. If you found the contents in this post or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{support me}, thanks \par}
\end{center}
\endgroup}
\begin{titlepage}
\titleCM
\end{titlepage}
\tableofcontents

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
\end{center}
\end{document}

>>>>

% Intended LaTeX compiler: pdflatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
       \usepackage{tikz}
       \usetikzlibrary{arrows,decorations.pathmorphing}
       \usetikzlibrary{backgrounds,positioning,fit,petri}
               \usepackage{tikz}
\author{Eason}
\date{\today}
\title{Walk Through the Petri-Net In TiKZ Tutorial}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Walk Through the Petri-Net In TiKZ Tutorial},
 pdfkeywords={},
 pdfsubject={Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Walk Through the Petri-Net In TiKZ Tutorial} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinetfinal.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

Analyze the Petri-Net tutorial in Chapter 3 of the TikZ manual line by line.

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/petrinet.pdf}
\end{center}

The code is shown as
\lstset{language=[LaTeX]TeX,label= ,caption= ,captionpos=b,firstnumber=1,numbers=left}
\begin{lstlisting}
\begin{tikzpicture}
  [node distance=1.3cm,on grid,>=stealth',bend angle=45,auto,
  every place/.style= {minimum size=6mm,thick,draw=blue!75,fill=blue!20},
  every transition/.style={thick,draw=black!75,fill=black!20},
  red place/.style= {place,draw=red!75,fill=red!20},
  every label/.style= {blue}]
  \node [place,tokens=1] (w1) {};
  \node [place] (c1) [below=of w1] {};
  \node [place] (s) [below=of c1,label=above:$s\le 3$] {};
  \node [place] (c2) [below=of s] {};
  \node [place,tokens=1] (w2) [below=of c2] {};
  \node [transition] (e1) [left=of c1] {}
  edge [pre,bend left] (w1)
  edge [post,bend right] (s)
  edge [post] (c1);
  \node [transition] (e2) [left=of c2] {}
  edge [pre,bend right] (w2)
  edge [post,bend left] (s)
  edge [post] (c2);
  \node [transition] (l1) [right=of c1] {}
  edge [pre] (c1)
  edge [pre,bend left] (s)
  edge [post,bend right] node[swap] {2} (w1);
  \node [transition] (l2) [right=of c2] {}
  edge [pre] (c2)
  edge [pre,bend right] (s)
  edge [post,bend left] node {2} (w2);

  \begin{scope}[xshift=6cm]
    \node [place,tokens=1] (w1') {};
    \node [place] (c1') [below=of w1'] {};
    \node [red place] (s1') [below=of c1',xshift=-5mm]
    [label=left:$s$] {};
    \node [red place,tokens=3] (s2') [below=of c1',xshift=5mm]
    [label=right:$\bar s$] {};
    \node [place] (c2') [below=of s1',xshift=5mm] {};
    \node [place,tokens=1] (w2') [below=of c2'] {};
    \node [transition] (e1') [left=of c1'] {}
    edge [pre,bend left] (w1')
    edge [post] (s1')
    edge [pre] (s2')
    edge [post] (c1');
    \node [transition] (e2') [left=of c2'] {}
    edge [pre,bend right] (w2')
    edge [post] (s1')
    edge [pre] (s2')
    edge [post] (c2');
    \node [transition] (l1') [right=of c1'] {}
    edge [pre] (c1')
    edge [pre] (s1')
    edge [post] (s2')
    edge [post,bend right] node[swap] {2} (w1');
    \node [transition] (l2') [right=of c2'] {}
    edge [pre] (c2')
    edge [pre] (s1')
    edge [post] (s2')
    edge [post,bend left] node {2} (w2');
  \end{scope}
  \begin{scope}[on background layer]
    \node (r1) [fill=black!10,rounded corners,fit=(w1)(w2)(e1)(e2)(l1)(l2)] {};
    \node (r2) [fill=black!10,rounded corners,fit=(w1')(w2')(e1')(e2')(l1')(l2')] {};
  \end{scope}
  \draw [shorten >=1mm,-to,thick,decorate,
  decoration={snake,amplitude=.4mm,segment length=2mm,
    pre=moveto,pre length=1mm,post length=2mm}]
  (r1) -- (r2) node [above=1mm,midway,text width=3cm,align=center]
  {replacement of the \textcolor{red}{capacity} by \textcolor{red}{two places}};
\end{tikzpicture}
\end{lstlisting}
\end{document}
